
\noindent
In the rapidly evolving world of microservices and multi-tenant applications, the demand for secure and scalable solutions for data management is higher than ever. This project aimed to meet that demand by developing a full-stack web application for managing configuration files used in distributed data pipelines. We used a range of modern technologies such as Next.js, NextAuth, Prisma, tRPC, and ChakraUI, to create a reliable and fast solution that fits the project's requirements. \\

\noindent
Next.js, a React-based web framework, was used for the front-end development of the application. Its powerful features, such as server-side rendering, ensured a fast and responsive user interface. NextAuth was used for authentication, ensuring the security of the application. Prisma facilitated the management of the database, while tRPC was used for efficient communication between the front-end and back-end of the application. Finally, ChakraUI, a modern UI framework, was used to build a visually appealing and user-friendly interface, enhancing the overall user experience. \\

\noindent 
Our application's main function was to validate JSON files with JSON schemas, ensuring that the data used by our services was safe and in line with our customers' needs. We also made it easy to create, maintain, and validate configuration files, reducing the chances of human error or misconfigurations. \\

\noindent
The project resulted in a reliable and scalable system for managing configuration files in a distributed data pipeline environment. While the solution requires additional work before it can be used in a production environment, the project laid a solid foundation for further development into a more complete solution fit for enterprise standards. The results of the project offer valuable research insights and a reliable product that can help developers store, edit, and validate JSON configuration file in cloud-based environments.



